COSC3500 \\ 2D Orbital Simulation Report

### 2018-10-19 reports/ms1_report.tex
Add more data

Strangely, $n = 16$ with \textit{Barnes-Hut} enabled took longer than expected, when compared to $n \in \{ 4, 8, 12 \}$. Further investigation is required.
\begin{figure}[b]
\caption{Scaling characteristics}
\centering
\label{fig:performance}
\includegraphics[width=\textwidth]{performance}
\end{figure}

@@

>>>>

Strangely, $n = 16$ with \textit{Barnes-Hut} enabled took longer than expected, when compared to $n \in \{ 4, 8, 12 \}$. Further investigation is required.

\begin{center}
\includegraphics[width=0.75\textwidth]{performance}
\end{center}

@@

Further evidence can be seen for this multiprocesing overhead hypothesis, where decreasing the total number of processes allocated to each CPU decreases time.

\includegraphics[width=14.2cm]{1024-cpusPerTask-tasksPerNode-n8tpn}

We can also see that \texttt{--ntasks-per-node=1} runs with consistently good performance. We'll drill into data where\texttt{--ntasks-per-node=1} and further analyse its scaling characteristics.
